---
title: "Different_comparisons_Ovarian_aging"
output: html_document
date: '2022-07-20'
---

```{r message= FALSE, warning= FALSE, echo=FALSE}
library("recount3")

ovarian_recount3 <- recount3::create_rse_manual(
  project = "OV",
  project_home = "data_sources/tcga",
  organism = "human",
  annotation = "gencode_v26",
  type = "gene"
)

ovarian_counts <- ovarian_recount3@assays@data@listData$raw_counts
```


before this make the meta information from TCGA's website as well as the information from above 

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
library(tibble)
library(ggplot2)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Initial_Comparisons_Menopause_Status/TCGA_meta.csv")
sampleNames <- sample_meta_data$From_Original_Order
Menopause_status <- sample_meta_data$Menopause_status
sampleTable <- data.frame(sampleName = sampleNames,
                          condition = Menopause_status)
sampleTable$condition <- factor(sampleTable$condition)
dds <- DESeqDataSetFromMatrix(ovarian_counts, sampleTable, ~condition)
dds <- DESeq(dds)
res <- results(dds)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
res_post_vs_pre <- results(dds, contrast=c("condition","Post-Menopause ","Pre-Menopause"))
```

```{r}
res_post_vs_pre
```

```{r}
summary(res_post_vs_pre)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
write.csv(res_post_vs_pre, "~/Desktop/results_post_vs_pre_aging_tcga.csv")
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
res_post_vs_meno <- results(dds, contrast=c("condition","Post-Menopause ","Menopause "))
```

```{r}
res_post_vs_meno
```

```{r}
summary(res_post_vs_meno)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
write.csv(res_post_vs_meno, "~/Desktop/results_post_vs_meno_aging_tcga.csv")
```

```{r}
res_pre_vs_meno <- results(dds, contrast=c("condition","Pre-Menopause", "Menopause "))
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
write.csv(res_pre_vs_meno, "~/Desktop/results_pre_vs_meno_aging_tcga.csv")
```

#now I have the p value <0.05 of each group and the one from my OG DeSeq2 analysis. 
#Venn Diagrams to show unique vs overlap

#imported in the ENSMBL ids and the Gene symbol columns in. All have been filtered to have
# p val <0.05 and remove NAs. 

```{r setup, include=FALSE}
library(ggVennDiagram)
library(ggplot2)
library(sf)
library(VennDiagram)
```

```{r}
results_post_vs_meno_aging_tcga <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Initial_Comparisons_Menopause_Status/TCGA_Menopause_Grouping1/Menopause_groups_no_decimals/post_vs_meno-no_decimal.csv")

results_post_vs_pre_aging_tcga <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Initial_Comparisons_Menopause_Status/TCGA_Menopause_Grouping1/Menopause_groups_no_decimals/pre_vs_post-no_decimal.csv")

results_pre_vs_meno_aging_tcga <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Initial_Comparisons_Menopause_Status/TCGA_Menopause_Grouping1/Menopause_groups_no_decimals/pre_vs_meno-no_decimal.csv")
```


```{r warning=FALSE, echo=FALSE}
post_vs_meno<- results_post_vs_meno_aging_tcga$ENSMBL
pre_vs_post<- results_post_vs_pre_aging_tcga$ENSMBL
pre_vs_meno<- results_pre_vs_meno_aging_tcga$ENSMBL
```
  

```{r, echo=FALSE}
x <- list(post_vs_meno= post_vs_meno, pre_vs_post= pre_vs_post, pre_vs_meno= pre_vs_meno)
venn <- Venn(x)
d <- process_data(venn)
d2 <- process_data(venn)

d2@region <- st_polygonize(d@setEdge)

col <- c("post_vs_meno" = "#482677FF", "pre_vs_post"= "#29AF7FFF", "pre_vs_meno"= "#33638DFF")

ggplot() +
geom_sf(aes(fill = name), data = venn_region(d2)) +
geom_sf(aes(color = name), data = venn_setedge(d)) +
geom_sf_text(aes(label = count), data = venn_region(d)) +
scale_color_manual(values = alpha(col, .7)) +
scale_fill_manual(values = alpha(col, .7)) +
theme_void()
```
```{r message= FALSE, warning= FALSE, echo=FALSE} 
library(VennDiagram)
#saving these groups 
Overlap_Aging_groups <- calculate.overlap(x = list(post_vs_meno, pre_vs_post, pre_vs_meno))
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
all_together <- Overlap_Aging_groups$a5
post_vs_meno_only <- Overlap_Aging_groups$a1
pre_vs_meno_only <- Overlap_Aging_groups$a7
pre_vs_post_only <- Overlap_Aging_groups$a3
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
write.csv(all_together, "~/Desktop/all_together.csv")
write.csv(post_vs_meno_only, "~/Desktop/post_vs_meno_only.csv")
write.csv(pre_vs_meno_only, "~/Desktop/pre_vs_meno_only.csv")
write.csv(pre_vs_post_only, "~/Desktop/pre_vs_post_only.csv" )
```


```{r warning=FALSE, echo=FALSE}
tgfb_file <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Menopause_TGFB_Family_Similarities_Results/Updated_TGFB_SuperFamily_Gene_list.csv")
tgfb <- tgfb_file$ENSMBL

aging_file <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Menopause_Aging_Genes_Similarity_Results/Aging_Gene_List.csv")
aging <- aging_file$ENSEMBL

angiongenesis_file <- read.csv("~/Documents/Mythreye_Lab/Asha/TCGA/Menopause_Angiogenesis_Genes_Similarity_Results/Angiogenesis_gene_list.csv")
angiogenesis <- angiongenesis_file$ENSEMBL
```


```{r, echo=FALSE}
x <- list("Post-Menopause vs Menopause"= post_vs_meno, "Post-Menopause vs Pre-Menopause"= pre_vs_post, "Pre-Menopause vs Menopause"= pre_vs_meno, "TGFB Super Family"= tgfb)
venn <- Venn(x)
d <- process_data(venn)
d2 <- process_data(venn)

d2@region <- st_polygonize(d@setEdge)

col <- c("Post-Menopause vs Menopause" = "#482677FF", "Post-Menopause vs Pre-Menopause"= "#29AF7FFF", "Pre-Menopause vs Menopause"= "#33638DFF", "TGFB Super Family"= "#75D054FF")

ggplot() +
geom_sf(aes(fill = name), data = venn_region(d2)) +
geom_sf(aes(color = name), data = venn_setedge(d)) +
geom_sf_text(aes(label = count), data = venn_region(d)) +
scale_color_manual(values = alpha(col, .7)) +
scale_fill_manual(values = alpha(col, .7)) +
theme_void()

ggsave("~/Desktop/Overlap.svg", plot = last_plot())
``` 


```{r message= FALSE, warning= FALSE, echo=FALSE}
library(VennDiagram)
#saving these groups 
Overlap_Aging_groups_TGFB <- calculate.overlap(x = list(post_vs_meno, pre_vs_post, pre_vs_meno, tgfb))

write.csv(Overlap_Aging_groups_TGFB$a10, "~/Desktop/post_vs_meno_TGFB.csv")

write.csv(Overlap_Aging_groups_TGFB$a8 , "~/Desktop/pre_vs_post_TGFB.csv")
```



```{r, echo=FALSE}
x <- list(post_vs_meno= post_vs_meno, pre_vs_post= pre_vs_post, pre_vs_meno= pre_vs_meno, Aging_Genes= aging)
venn <- Venn(x)
d <- process_data(venn)
d2 <- process_data(venn)

d2@region <- st_polygonize(d@setEdge)

col <- c("post_vs_meno" = "#482677FF", "pre_vs_post"= "#29AF7FFF", "pre_vs_meno"= "#33638DFF", "Aging_Genes"= "#75D054FF")

ggplot() +
geom_sf(aes(fill = name), data = venn_region(d2)) +
geom_sf(aes(color = name), data = venn_setedge(d)) +
geom_sf_text(aes(label = count), data = venn_region(d)) +
scale_color_manual(values = alpha(col, .7)) +
scale_fill_manual(values = alpha(col, .7)) +
theme_void()
```
```{r message= FALSE, warning= FALSE, echo=FALSE} 
library(VennDiagram)
#saving these groups 
Overlap_Aging_groups <- calculate.overlap(x = list(post_vs_meno, pre_vs_post, pre_vs_meno, aging))

write.csv(Overlap_Aging_groups$a10, "~/Desktop/post_vs_meno_aging_genes.csv")

write.csv(Overlap_Aging_groups$a7 , "~/Desktop/pre_vs_meno_vs_pre_vs_post_aging_genes.csv")

write.csv(Overlap_Aging_groups$a8, "~/Desktop/post_vs_pre_aging_genes.csv")

write.csv(Overlap_Aging_groups$a11 , "~/Desktop/pre_vs_post_vs_post_vs_meno_aging_genes.csv")
```


```{r, echo=FALSE}
x <- list(post_vs_meno= post_vs_meno, pre_vs_post= pre_vs_post, pre_vs_meno= pre_vs_meno, Angiogenesis_Genes= angiogenesis)
venn <- Venn(x)
d <- process_data(venn)
d2 <- process_data(venn)

d2@region <- st_polygonize(d@setEdge)

col <- c("post_vs_meno" = "#482677FF", "pre_vs_post"= "#29AF7FFF", "pre_vs_meno"= "#33638DFF", "Angiogenesis_Genes"= "#75D054FF")

ggplot() +
geom_sf(aes(fill = name), data = venn_region(d2)) +
geom_sf(aes(color = name), data = venn_setedge(d)) +
geom_sf_text(aes(label = count), data = venn_region(d)) +
scale_color_manual(values = alpha(col, .7)) +
scale_fill_manual(values = alpha(col, .7)) +
theme_void()
``` 

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(VennDiagram)
#saving these groups 
Overlap_Angiogensis_groups <- calculate.overlap(x = list(post_vs_meno, pre_vs_post, pre_vs_meno, angiogenesis))

write.csv(Overlap_Angiogensis_groups$a10, "~/Desktop/post_vs_meno_angiogenesis_genes.csv")

write.csv(Overlap_Angiogensis_groups$a7 , "~/Desktop/pre_vs_meno_vs_pre_vs_post_angiogenesis_genes.csv")

write.csv(Overlap_Angiogensis_groups$a8, "~/Desktop/post_vs_pre_angiogenesis_genes.csv")

write.csv(Overlap_Angiogensis_groups$a11 , "~/Desktop/pre_vs_post_vs_post_vs_meno_angiogenesis_genes.csv")

write.csv(Overlap_Angiogensis_groups$a2 , "~/Desktop/pre_vs_meno_angiogenesis_genes.csv")
```

Gene overlaps/ Genes of Interest

TGFB Menopause Status 

Pre vs Post Overlap 
```{r}
col = c("Menopause "= "#481567FF", "Pre-Menopause"= "#2D708EFF", "Post-Menopause "= "#29AF7FFF")
```


```{r}
counts <- counts(dds['ENSG00000135503.12',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of ACVR1B")
q
ggsave("~/Desktop/TGFB2.svg", plot = last_plot())
```

```{r}
counts <- counts(dds['ENSG00000123612.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of ACVR1C")
q
ggsave("~/Desktop/ACVR1C.svg", plot = last_plot())
```

```{r}
counts <- counts(dds['ENSG00000135414.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of GDF11")
q
ggsave("~/Desktop/GDF11.svg", plot = last_plot())
```
```{r}
counts <- counts(dds['ENSG00000143869.6',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause "))
q <- q + labs(y = "Normalized Counts ", title = "Expression of GDF7")
q
```
```{r}
counts <- counts(dds['ENSG00000092969.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of TGFB2")
q
ggsave("~/Desktop/TGFB2.svg", plot = last_plot())
```
```{r}
counts <- counts(dds['ENSG00000090539.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of CHRD")
q
ggsave("~/Desktop/CHRD.svg", plot = last_plot())
```
```{r}
counts <- counts(dds['ENSG00000243709.1',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of LEFTY1")
q
ggsave("~/Desktop/LEFTY1.svg", plot = last_plot())
```
```{r}
counts <- counts(dds['ENSG00000156574.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of NODAL")
q
ggsave("~/Desktop/NODAL.svg", plot = last_plot())
```



```{r}
counts <- counts(dds['ENSG00000103888.16',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Pre-Menopause", "Menopause ", "Post-Menopause ")) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.title = element_text(size=22))
q <- q + labs(y = "Normalized Counts ", title = "Expression of CEMIP")
q
ggsave("~/Desktop/NODAL.svg", plot = last_plot())
```